A Review of Lossless Data Compression Methods

### 2018-11-19 paper.tex
Add basic FLAC information.

Since knowing the structure of a given input can allow the
construction of a more efficient data compression scheme, it is
worthwhile to study some compression scheme which is specifically
designed to store a particular type of data. In this secion I will
describe the structure and function of the Free Lossless Audio Codec,
known more commonly by its acronym FLAC, a popular format for
high-fidelity audio storage.

>>>>

Since knowing the structure of a given input can allow the
construction of a more efficient data compression scheme, it is
worthwhile to study some compression scheme which is specifically
designed to store a particular type of data. In this secion I will
describe the structure and function of the Free Lossless Audio Codec,
known more commonly by its acronym FLAC, a popular format for
high-fidelity audio storage. \cite{flac}

Since FLAC is designed exclusively for storing high-fidelity audio
data, it is able to exploit characteristics specific to sound in order
to achieve a better compression ratio than a simple general purpose
compression scheme would be able to. For instance, FLAC's designers
realize that stereo sound streams often correlate very closely. As
such, FLAC allows the compressor to encode input in multiple ways;
left and right can be encoded independently, or as ``mid'' and
``side'' channels, where the mid channel is an average of the left and
right channels and the side is the difference of the two. For highly
correlated left/right channels, this encoding can result in
significant lossless compression gains.

The primary means of compression, however, is through model/residual
coding. For each block of raw input, the FLAC compressor tries to fit
the signal to a parameterized function, such as a polynomial for
instance, and then stores the function. It then computes the
residuals, or the differences between the raw audio signal and the
parameterized function at each sample. This residual data has a
particular distribution which is efficiently stored using a specific
form of Huffman codes, called Rice codes. \cite{flac}
